Rank Verification for Exponential Families

### 2016-07-08 verifying-winner.tex
minor fixes #2

\begin{proof}
The type I error --- the probability of incorrectly declaring any non-best to be the best --- is
\begin{equation}
\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],
\label{eq:marginal}
\end{equation}
where $j^*$ is the best (fixed when the distribution is determined). The probability above is taken over all distributions where $j^*$ is the best. However, since there is exactly one winner at all times (recall that ties are broken at all times), it is sufficient to bound $\PP_{j^* \text{ is the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right]$, for each $j \ne j^*$. Since $j^*$ being the best implies that $j$ is not the best, it is, in turn, sufficient to show that
$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right].$$

@@

As the construction of this test follows \citet{Fithian:2014ws}, it is also a UMPU selective level-$\alpha$ test.

The selective type I error we opted to control for Procedure 1 offers the conventional, marginal type I error rate, as shown in \eqref{eq:marginal}. More precisely with our notation in the proof,
\begin{equation}
\PP_{H_{01}}\left[\text{reject } H_{01}\right] = \PP_{H_{01}}\left[\text{Winner is } 1\right] \PP_{H_{01}}\left[\text{reject } H_{01} \;\middle|\; \text{Winner is } 1\right] \le \frac{n-1}{n} \alpha,
\label{eqn:marginal}
\end{equation}
because, under the hypothesis $H_{01}$, the probability of $1$, which is not the best population, winning is at most $\frac{n-1}{n}$. Selective type I error rate control provides more than just marginal type I error rate control. \citet{Fithian:2015uj} has shown that it helps controlling familywise error rate, which we will utilize in \Cref{sec:stepdown}.

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$. Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than \citeauthor{Gupta:1967wg}'s test.

>>>>

\begin{proof}
The type I error --- the probability of incorrectly declaring any non-best to be the best --- is
$$\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \PP\left[\text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \PP\left[j \text{ wins}\right],$$
where $j^*$ is the best (fixed when the distribution is determined). The probability above is taken over all distributions where $j^*$ is the best. However, since there is exactly one winner at all times (recall that ties are broken at all times), it is sufficient to bound $\PP_{j^* \text{ is the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right]$, for each $j \ne j^*$. Since $j^*$ being the best implies that $j$ is not the best, it is, in turn, sufficient to show that
$$\PP_{j \text{ is not the best}}\left[ \text{declare } j \text{ best} \;\middle|\; j \text{ wins}\right] \le \alpha,$$
giving us
\begin{equation}
\PP\left[\bigcup_{j \ne j^*} \text{declare } j \text{ best}\right] \le \sum_{j \ne j^*} \alpha \cdot \PP\left[j \text{ wins}\right] \le \frac{n-1}{n} \alpha.
\label{eq:marginal}
\end{equation}

@@

As the construction of this test follows \citet{Fithian:2014ws}, it is also a UMPU selective level-$\alpha$ test. The selective type I error we opted to control for Procedure 1 offers more than just marginal type I error rate control. \citet{Fithian:2015uj} has shown that it helps controlling familywise error rate, which we will utilize in \Cref{sec:stepdown}.

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For their method, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \eqref{eq:marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$. Their test coincides with our test at $n = 2$; however as $n$ grows, the selective test shows significantly more power than \citeauthor{Gupta:1967wg}'s test.
